Learning words by recursive pragmatic reasoning about other agents

### 2013-05-31 praglearn.tex
revisions on simulation figures and on model section

\title{Learning words by recursive pragmatic reasoning about other agents: The blessing of social anxiety}

@@

\begin{abstract}
  Adult language users are remarkably good at making inferences about speakers' intentions in context, and children learning their native language also display substantial pragmatic skill in acquiring the meanings of unknown words. While pragmatic inference and word learning have both been characterized in probabilistic terms, no current models make appropriate inferences about the meanings of words in pragmatically-rich inferential contexts. We describe a model in which language learners assume that they jointly approximate a shared, external lexicon and reason recursively about the goals of others in using this lexicon. This model captures phenomena in word learning and pragmatic inference; it additionally leads to insights about the emergence of communicative systems in conversation and the mechanisms by which pragmatic inferences become incorporated into word meanings.
\end{abstract}

%\section{Introduction}

@@

The goal of our current work is to investigate the possibilities for integrating models of recursive pragmatic reasoning with models of language learning, with the hope of capturing phenomena in both domains. We begin by describing previous models in each domain as well as proposals for bringing the two together. We next simulate findings from the domains of pragmatic inference, word learning, and their intersection (summarized in Table \ref{tab:results}). We end by discussing the implications of our results for work on language change.

@@

Consider a simple communicative game: two participants each,
separately, view identical arrays of objects. On the
\textit{Speaker's} screen, one object is highlighted; their goal is to
get the \textit{Listener} to click on this item. To do this, they have
available a fixed, finite set of words; they must pick one. The
Listener then receives this word, and attempts to guess which object
the Speaker meant by it.

When modelling human behaviour, it's useful to begin with optimal models; this has the advantage that when we are then forced to deviate from the purely rational approach, it's generally in a theoretically interpretable way. However, multi-agent interactions are notoriously difficult to model in a normative fashion without falling prey to paradox. For example, consider a simple model of the agents in the above game. First we define a \textit{literal listener} agent denoted $L_0$. This agent has a \textit{lexicon} which probabilistically maps words to meanings; specifically, it assigns each word $w$ a vector describing the extent to which this word provides evidence for each object\footnote{In this model, words refer directly to objects; more realistically, words should refer to some sort of abstract semantic features, which in turn refer to objects. However, our simplification is without loss of generalization, because we can interpret our model as marginalizing over such a representation, with our literal $P_\lex(\obj | \word) = \sum_\text{features} P(\obj | \text{features}) P_\lex(\text{features} | \word)$.}. Each entry in the vector is in $(0, 1)$, and together they sum to 1:
\begin{align*}
P_{L_0}(\obj | \word, \lex) &\propto \lex(\word, \obj) \times \prior.
\end{align*}
Confronted with such a listener, a rational (but noisy) speaker should attempt to choose a word which soft-maximizes the probability that the listener will assign to the target object -- possibly modulated by the effort or cost associated with producing this word:
\begin{align*}
P_{S_1}(\word | \obj, \lex) &\propto \exp\Big(\lambda \big(\log P_{L_0}(\obj | \word, \lex) - \text{cost}(\word)\big)\Big).
\end{align*}
But if this is how the speaker will behave, then it's not rational for a listener to implement the $L_0$ strategy. Instead, to best determine what object was intended, they should use Bayes rule to invert the speaker's decision procedure:
\begin{align*}
P_{L_2}(\obj | \word, \lex) &\propto P_{S_1}(\word | \obj, \lex) \times \prior.
\end{align*}
Now the paradox becomes apparent. Given such a listener, it's no longer rational for the speaker to implement strategy $S_1$; instead, they should implement strategy $S_3$ which soft-maximizes $P_{L_2}$ instead of $P_{L_0}$. And then the listener ought to implement $L_4$, and so on.

One computationally expensive option is to continue iterating such strategies until one reaches a fixed point equilibrium. But, while this guarantees each agent will behave normatively given the other agent's strategy, there is no guarantee that such strategies will be near the system's global optimum; equilibrium strategies make up only a small subspace of all possible strategies. Nor is there much evidence the humans find such equilibria; their behaviour in language games (and in other games XX p-beauty) can be well-modeled as implementing $S_n$ or $L_n$ for some small $n$ \cite{frank2012}. This paradox, then, is averted by simply recursing a small, finite number of times. The consequence is that one agent, implementing $S_n$, say, can be fully rational, while the other, implementing $L_{n-1}$, is nearly rational -- they're off by only a single recursion.

But as soon as we attempt to add learning to this model, new paradoxes arise. Suppose the listener is a young child who is uncertain about the lexicon their partner is using. The obvious solution is for them to place a prior on the lexicon; they then update their posterior based on whatever utterances and contextual cues they observe, and in the mean time interpret each utterance by making their best guess, marginalizing out this uncertainty. This basic structure is the essence of previous models of Bayesian word learning (e.g., \cite{frank2009}). But when combined with the recursive pragmatic model, a new question arises: Given such a listener, what model should the speaker use? A rational speaker attempts to maximize the listener's likelihood of understanding, so if an uncertain listener interpets by marginalizing over some posterior, then a knowledgeable speaker should calculate this posterior and marginalize themselves, before applying the soft-max decision rule. But this means that the speaker is not using any particular lexicon at all, and a rational learning listener should therefore not be trying to infer the speaker's lexicon. In fact, such an uncertain listener's uncertainty dissolves; they may not know the lexicon, but they do know their posterior over the lexicon -- and because this is all that the speaker cares about, there is nothing for the listener to learn from the speaker's behaviour.

Of course, in reality both parties will generally have some uncertainty, which makes things even worse. If we start from an uncertain listener with a prior over lexicons, then a first-level uncertain speaker needs a prior over priors on lexicons, a second-level uncertain listener needs a prior over priors over priors, etc. The original $L_0 \rightarrow S_1 \rightarrow \dots$ recursion was bad enough, but at least each step had a constant cost. This new recursion produces hyper$^n$-distributions for which inference almost immediately becomes intractable even in principle, since the dimensionality of the learning problem increases with each step. Yet, without this addition of new uncertainty at each level, the model would dissolve back into certainty as in the previous paragraph, making learning impossible.

And one final problem is that in real life, the same agents alternate between speaking and listening, and generally use the same language to do so. There's nothing in these models to ensure this, and this is somehow reasonable: in principle, so long as I as a listener have a good model of you as a speaker, and I as a speaker have a good model of you as a listener, then we can communicate perfectly well, even if we use entirely different languages depending on who is talking. Yet most people do in fact speak languages that they have learned by listening to others, which suggests an additional constraint that should somehow be incorporated into learning: as I build a model of you as a speaker, it should also affect my model of myself as a speaker.

\subsection{A ``social anxiety'' model of pragmatic word learning}

Clearly we must deviate from pure normativity -- but how? Here, we propose to resolve the above problems with a model of speakers and listeners as rational agents afflicted by a kind of social anxiety. Specifically, each agent assumes: (a) There is some single, specific literal lexicon which everyone should be using, (b) and everyone else knows this lexicon, and believes that I know it as well, (c) but in fact I don't. Assumption (a) explains the lexicographer's illusion: naive language users are convinced and will vociferously that words have specific meanings, even though these meanings are unobservable to everyone who purportedly uses them. It also explains why children speak the language they hear, since observing your behaviour now gives me data about not just \textit{your} lexicon, but \textit{the} lexicon. Assumption (b) avoids the explosion of hyper$^n$-distributions: if agent $n$ knows the lexicon, they assume that all lower agents do as well, reducing to the original tractable model without uncertainty. And assumption (c) introduces a limited form of uncertainty, and thus the potential for learning. Everything else follows by applying standard Bayesian reasoning given these assumptions.

Formally, let an unadorned $L$ and $S$ denote our socially-anxious listener and speaker. $L$ inverts their marginal distribution over the speaker; $S$ soft-maximizes their marginal distribution over the listener. With $L_i$ and $S_i$ as above, this gives:
\begin{align*}
  P_L(\obj | \word) &= P_{S_{n-1}}(\word | \obj, \text{$L$'s data}) \times \prior \\
    &= \sum_\lex P_{S_{n-1}}(\word | \obj, \lex) \times P(\lex | \text{$L$'s data}) \times \prior \\
    &= P_{L_n}(\obj | \word, \text{$L$'s data}). \\
  P_S(\word | \obj) &\propto \exp\Big(\lambda \big(\log P_{L_n}(\obj | \word, \text{$S$'s data}) - \text{cost}(\word)\big)\Big).
\end{align*}
Here $L$'s data consists of $S$'s utterances together with whatever other information $L$ may have about their meaning (e.g.~from contextual clues) -- but by assumption (b), $L$ treats these as utterances as samples from the knowledgeable speaker $S_{n-1}$, not $S$, and thus as being informative about the lexicon. Similarly, $S$ may observe $L$'s interpretations of various utterances, and will treat these as samples from $L_n$, not $L$.
In several important cases, these assumptions are as close to rational as possible within the finite-recursion framework. If $L_n(\obj | \word, \text{$S$'s data})$ and $L_n(\obj | \word, \text{$L$'s data})$ coincide, then  $S$ is fully normative and $L$ is off by only a single recursion. This in particular includes all previous experiments using this pragmatic reasoning framework, which considered only single-turn interactions where $\text{$L$'s data} = \text{$S$'s data} = \emptyset$. Alternatively, if one agent has enough data that their uncertainty is effectively non-existent, then it becomes normative for their partner to treat them as being fully knowledgeable, and this is a reasonable description of the child language learning case. In general, though, in arbitrary multi-turn interactions in which both agents have non-trivial uncertainty, this model induces complex and non-normative learning dynamics. In the remainder of this paper, we computationally investigate the model's behaviour in all three situations.\footnote{In our simulations throughout, we somewhat arbitrarily set $n = 2$ (the minimal value that produces all the qualitative phenomena), $\lambda = 3$, and assume that all agents have shared priors on the lexicon and full knowledge of the cost function. Inference is via importance sampling.}

@@

In this section, we describe the coverage of our pragmatic learning model on phenomena previously investigated with the pragmatics and word learning components of the model. To summarize these simulations: the pragmatic learning model reproduces previous findings and provides some new insights into the ``disambiguation'' phenomenon described above.

\begin{table}[t]
\label{tab:results}
\begin{center}
\begin{tabular}{lccccc}
\toprule
Phenomenon & Ref. & WL & PI & PI+U & This work \\
\midrule
Interpreting specificity implicature & \cite{grice1975} &  & x &x & x\\
Interpreting Horn implicature & \cite{horn1984} & &  & x& x\\
Cross-situational learning & \cite{smith2008} & x& & & x \\
Disambiguating new words using old words & \cite{markman1988} &x  & & & x \\
Disambiguation without mapping & \cite{horst2008} &  & & & x \\
Emergence of novel \& efficient communicative systems & \cite{galantucci2005} & & & & x \\
Lexicalization of Horn implicature & \cite{horn1984} & & & & x \\
Lexicalization of specificity implicature & \cite{levinson2000} & & & & x \\
\hline
\end{tabular}
\end{center}
\caption{Empirical results and references. WL refers to the word learning model of \cite{frank2009}; PI refers to the recursive pragmatic inference model of \cite{frank2012}; PI+U refers to the pragmatic inference model of \cite{bergen2012} which includes lexical uncertainty, marginalizes it out, and then recurses.}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{figures/emergence2x2-1.pdf}
\includegraphics[width=0.48\textwidth]{figures/emergence2x2-3.pdf} \\
\includegraphics[width=0.48\textwidth]{figures/emergence3x3-0.pdf}
\includegraphics[width=0.48\textwidth]{figures/emergence3x3-1.pdf} \\
\caption{\label{fig:emergence} Simulations of two learning pragmatic agents playing a naming game. At each stage, $S$ and $L$ have different, possibly contradictory posteriors over the literal lexicon. From these posteriors we derive the probability $P(\text{$L$ understands $S$})$ (marginalizing over target objects and word choices), and also depict graphically $S$'s model of the listener, $P_{L_n}(\obj | \word, \text{$S$'s data})$, and $L$'s actual model, $P_{L_n}(\obj | \word, \text{$L$'s data})$.}
\end{figure}

>>>>

\title{Learning words by recursive pragmatic reasoning about other agents}
% : The blessing of social anxiety - not a huge fan of colon titles

@@

\begin{abstract}
Language users are remarkably good at making inferences about speakers' intentions in context, and children learning their native language also display substantial pragmatic skill in acquiring the meanings of unknown words. While pragmatic inference and word learning have both been characterized in probabilistic terms, no current models make appropriate inferences about the meanings of words in pragmatically-rich inferential contexts. We describe a model in which language learners assume that they jointly approximate a shared, external lexicon and reason recursively about the goals of others in using this lexicon. This model captures phenomena in word learning and pragmatic inference; it additionally leads to insights about the emergence of communicative systems in conversation and the mechanisms by which pragmatic inferences become incorporated into word meanings.
\end{abstract}

\section{Introduction}

@@

The goal of our current work is to investigate the possibilities for integrating models of recursive pragmatic reasoning with models of language learning, with the hope of capturing phenomena in both domains. We begin by describing previous models in each domain as well as proposals for bringing the two together. We next simulate findings from the domains of pragmatic inference, word learning, and their intersection. We end by discussing the implications of our results for work on language change.

@@

We model a standard communication game \cite{krauss1964,clark1986}: two participants each,
separately, view identical arrays of objects. On the \textit{Speaker's} screen, one object is highlighted; their goal is to get the \textit{Listener} to click on this item. To do this, they have available a fixed, finite set of words; they must pick one. The Listener then receives this word, and attempts to guess which object
the Speaker meant by it. In the psychology literature, as in real-world interactions, games are typically iterated; one view of our contribution here is as a generalization of one-shot models \cite{frank2012,bergen2012} to the iterated context.

\subsection{Paradoxes in optimal models of pragmatic learning}
% When modelling human behaviour, it's useful to begin with optimal models; this has the advantage that when we are then forced to deviate from the purely rational approach, it's generally in a theoretically interpretable way. However, 
Multi-agent interactions are difficult to model in a normative or optimal framework without falling prey to paradox. For example, consider a simple model of the agents in the above game. First we define a \textit{literal listener} $L_0$. This agent has a \textit{lexicon} which probabilistically maps words to meanings; specifically, it assigns each word $w$ a vector describing the extent to which this word provides evidence for each object\footnote{We assume words refer directly to objects, rather than to abstract semantic features. Our simplification is without loss of generalization, however, because we can interpret our model as marginalizing over such a representation, with our literal $P_\lex(\obj | \word) = \sum_\text{features} P(\obj | \text{features}) P_\lex(\text{features} | \word)$.}. Each entry in the vector is in $(0, 1)$, and together they sum to 1:
\begin{align*}
P_{L_0}(\obj | \word, \lex) &\propto \lex(\word, \obj) \times \prior.
\end{align*}
Confronted with such a listener, a probabilistically rational speaker should attempt to choose a word which soft-maximizes the probability that the listener will assign to the target object---modulated by the effort or cost associated with producing this word:
\begin{align*}
P_{S_1}(\word | \obj, \lex) &\propto \exp\Big(\lambda \big(\log P_{L_0}(\obj | \word, \lex) - \text{cost}(\word)\big)\Big).
\end{align*}
But given this speaker, then the naive $L_0$ strategy is not optimal. Instead, listeners should use Bayes rule to invert the speaker's decision procedure \cite{frank2012}:
\begin{align*}
P_{L_2}(\obj | \word, \lex) &\propto P_{S_1}(\word | \obj, \lex) \times \prior.
\end{align*}
Now the paradox becomes apparent. Given such a listener, it is no longer optimal for speakers to implement strategy $S_1$; instead, they should implement strategy $S_3$ which soft-maximizes $P_{L_2}$ instead of $P_{L_0}$. And then listeners ought to implement $L_4$, and so on.

One computationally expensive option is to continue iterating such strategies until reaching a fixed point equilibrium. While this strategy guarantees that each agent will behave normatively given the other agent's strategy, there is no guarantee that such strategies will be near the system's global optimum; equilibrium strategies make up only a small subspace of all possible strategies. Nor is there much evidence the humans find such equilibria; their behaviour in language games (and in other games \cite{camerer2004}) can be well-modeled as implementing $S_n$ or $L_n$ for some small $n$ \cite{frank2012}. Following this work, we  recurse a finite (small) number of times. The consequence is that one agent, implementing $S_n$, is fully optimal with respect to the game, while the other, implementing $L_{n-1}$, is nearly optimal---off by only a single recursion.

As soon as we attempt to add uncertainty about the meanings of words to such a model, new paradoxes arise. Suppose the listener is a young child who is uncertain about the lexicon their partner is using. The obvious solution is for them to place a prior on the lexicon; they then update their posterior based on whatever utterances and contextual cues they observe, and in the mean time interpret each utterance by making their best guess, marginalizing out this uncertainty. This basic structure is captured in previous models of Bayesian word learning \cite{frank2009}. But when combined with the recursive pragmatic model, a new question arises: Given such a listener, what model should the speaker use? A rational speaker attempts to maximize the listener's likelihood of understanding, so if an uncertain listener interpets by marginalizing over some posterior, then a knowledgeable speaker should calculate this posterior and marginalize themselves. But then the speaker is not using any particular lexicon at all, and a rational learning listener should therefore not be trying to infer the speaker's lexicon.\footnote{Of course, in reality both parties will generally have some uncertainty, making the situation even worse. If we start from an uncertain listener with a prior over lexicons, then a first-level uncertain speaker needs a prior over priors on lexicons, a second-level uncertain listener needs a prior over priors over priors, etc. The original $L_0 \rightarrow S_1 \rightarrow \dots$ recursion was bad enough, but at least each step had a constant cost. This new recursion produces hyper$^n$-distributions for which inference almost immediately becomes intractable even in principle, since the dimensionality of the learning problem increases with each step. Yet, without this addition of new uncertainty at each level, the model would dissolve back into certainty as in the previous paragraph, making learning impossible.}% In fact, such an uncertain listener's uncertainty dissolves; they may not know the lexicon, but they do know their posterior over the lexicon -- and because this is all that the speaker cares about, there is nothing for the listener to learn from the speaker's behaviour.

To add insult to injury, one final problem is that there is nothing constraining speaker and listener to use the same language under this model. In principle, so long as the listener has a good model of the speaker, and the speaker has a good model of the listener, then communication succeeds. This result clearly presents a dramatic mismatch to typical human communication, which almost never proceeds with distinct languages spoken by each participant.

% . Yet most people do in fact speak languages that they have learned by listening to others, which suggests an additional constraint that should somehow be incorporated into learning: as I build a model of you as a speaker, it should also affect my model of myself as a speaker.

\subsection{A conventionality-based model of pragmatic word learning}

We resolve the problems described above by assuming that speakers and listeners deviate from normative behavior by assuming a conventional lexicon. 
% Clearly we must deviate from pure normativity -- but how? Here, we propose to resolve the above problems with a model of speakers and listeners as rational agents afflicted by a kind of social anxiety. 
Each agent assumes: (a) There is some single, specific literal lexicon which everyone should be using, (b) and everyone else knows this lexicon, and believes that I know it as well, (c) but in fact I don't. These assumptions instantiate a kind of ``social anxiety'' in which agents are all trying to learn the correct lexicon that they assume everyone else knows.

Assumption (a) corresponds to the lexicographer's illusion: Naive language users will argue vociferously that words have specific meanings, even though these meanings are unobservable to everyone who purportedly uses them. It also explains why learners speak the language they hear (rather than some private language that they assume listeners will eventually learn): Under assumption (a), observing other speakers' behaviour provides data about not just that speaker's idiosyncratic lexicon, but the consensus lexicon. Assumption (b) avoids the explosion of hyper$^n$-distributions described above: If agent $n$ knows the lexicon, they assume that all lower agents do as well, reducing to the original tractable model without uncertainty. And assumption (c) introduces a limited form of uncertainty, and thus the potential for learning. 
% Everything else follows by applying standard Bayesian reasoning given these assumptions.

Formally, let an unadorned $L$ and $S$ denote our socially-anxious listener and speaker. $L$ inverts their marginal distribution over the speaker; $S$ soft-maximizes their marginal distribution over the listener. With $L_i$ and $S_i$ as above, this gives:
\begin{align*}
  P_L(\obj | \word) &= P_{S_{n-1}}(\word | \obj, \text{$L$'s data}) \times \prior \\
    &= \sum_\lex P_{S_{n-1}}(\word | \obj, \lex) \times P(\lex | \text{$L$'s data}) \times \prior \\
    &= P_{L_n}(\obj | \word, \text{$L$'s data}). \\
  P_S(\word | \obj) &\propto \exp\Big(\lambda \big(\log P_{L_n}(\obj | \word, \text{$S$'s data}) - \text{cost}(\word)\big)\Big).
\end{align*}
Here $L$'s data consists of $S$'s utterances together with whatever other information $L$ may have about their meaning (e.g.~from contextual clues). By assumption (b), $L$ treats these as utterances as samples from the knowledgeable speaker $S_{n-1}$, not $S$, and thus as being informative about the lexicon. Similarly, $S$ may observe $L$'s interpretations of various utterances, and will treat these as samples from $L_n$, not $L$.

In several important cases, these assumptions are as close to rational as possible within the finite-recursion framework. If $L_n(\obj | \word, \text{$S$'s data})$ and $L_n(\obj | \word, \text{$L$'s data})$ coincide, then  $S$ is fully normative and $L$ is off by only a single recursion. This case in particular includes all previous experiments using this pragmatic reasoning framework, which considered only single-turn interactions where $\text{$L$'s data} = \text{$S$'s data} = \emptyset$. Alternatively, if one agent has enough data that their uncertainty is effectively non-existent, then it becomes normative for their partner to treat them as being fully knowledgeable, and this is a reasonable description of the child language learning case. In general, though, in arbitrary multi-turn interactions in which both agents have non-trivial uncertainty, this model induces complex and non-normative learning dynamics. In the remainder of this paper, we investigate the model's behaviour in all three situations.\footnote{In our simulations throughout, we somewhat arbitrarily set $n = 2$ (the minimal value that produces all the qualitative phenomena), $\lambda = 3$, and assume that all agents have shared priors on the lexicon and full knowledge of the cost function. Inference is via importance sampling.}

@@

\begin{table}[t]
\label{tab:results}
\begin{center}
\begin{tabular}{lccccc}
\toprule
Phenomenon & Ref. & WL & PI & PI+U & PIL \\
\midrule
Interpreting specificity implicature & \cite{grice1975} &  & x &x & x\\
Interpreting Horn implicature & \cite{horn1984} & &  & x& x\\
Cross-situational learning & \cite{smith2008} & x& & & x \\
Disambiguating new words using old words & \cite{markman1988} &x  & & & x \\
Disambiguation without mapping & \cite{horst2008} &  & & & x \\
Emergence of novel \& efficient communicative systems & \cite{galantucci2005} & & & & x \\
Lexicalization of Horn implicature & \cite{horn1984} & & & & x \\
Lexicalization of specificity implicature & \cite{levinson2000} & & & & x \\
\hline
\end{tabular}
\end{center}
\caption{Empirical results and references. WL refers to the word learning model of \cite{frank2009}; PI refers to the recursive pragmatic inference model of \cite{frank2012}; PI+U refers to the pragmatic inference model of \cite{bergen2012} which includes lexical uncertainty, marginalizes it out, and then recurses. Our current model is referred to here as PIL, or pragmatic inference and learning.}
\end{table}

We begin by applying the model described above to a set of one-shot pragmatic inference games that have been well-studied in linguistics \cite{grice1975,horn1984} and are addressed by previous one-shot models of pragmatic inference \cite{frank2012,bergen2012}. These situations set the stage for simulations investigating how learning proceeds in iterated versions of such games, described in the following section. Results captured by our model and previous models are summarized in Table \ref{tab:results}.

% In this section, we describe the coverage of our pragmatic learning model on phenomena previously investigated with the pragmatics and word learning components of the model. To summarize these simulations: the pragmatic learning model reproduces previous findings and provides some new insights into the ``disambiguation'' phenomenon described above.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.98\textwidth]{figures/emergence-composite.pdf}
% \includegraphics[width=0.48\textwidth]{figures/emergence2x2-1.pdf}
% \includegraphics[width=0.48\textwidth]{figures/emergence2x2-3.pdf} \\
% \includegraphics[width=0.48\textwidth]{figures/emergence3x3-0.pdf}
% \includegraphics[width=0.48\textwidth]{figures/emergence3x3-1.pdf} \\
\caption{\label{fig:emergence} Simulations of two pragmatic agents playing a naming game. Each panel shows two representative simulation runs, with run 1 chosen to show strong convergence and run 2 chosen to show relatively weaker convergence. At each stage, $S$ and $L$ have different, possibly contradictory posteriors over the conventional, consensus lexicon. From these posteriors we derive the probability $P(\text{$L$ understands $S$})$ (marginalizing over target objects and word choices), and also depict graphically $S$'s model of the listener, $P_{L_n}(\obj | \word, \text{$S$'s data})$, and $L$'s actual model, $P_{L_n}(\obj | \word, \text{$L$'s data})$. }
\end{figure}
